Detecting Facial Expressions in Professional Tennis Matches

### 2017-01-19 Report06-12.Rmd
Manual full versions
Report Changes,
overlay plot colouring

setwd("C:/Users/steff/Github/face-recognition")

@@

      faceData <- faceData %>%
        mutate(x1 = minX, x2 = minX, x3 = maxX, x4 = maxX, x5 = minX,
               y1 = minY, y2 = maxY, y3 = maxY, y4 = minY, y5 = minY) %>%
        gather(corner, boxPos, x1:y5) %>%
        mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
        select(-corner) %>% spread(posCoord, boxPos)

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData)
    }
  return(p)
  }
}

@@

# change this to facesVenn with binary information
ALLmetaIMGFaces<-ALLmetaIMG%>%
  filter(!is.na(boxID)) %>% 
  dplyr::select(-ID, -facecounter)%>%
  mutate(fileID = as.numeric(factor(file))) %>%
  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))

@@

```{r Trial-Image, caption="This is a player", message=TRUE, warning=TRUE, anchor="figure"}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, ALLmetaIMG, matchBox = FALSE)
```

@@

@@

@@

`r figr("Face-Bounding-Box-Upset", TRUE, type="Figure")` Bar Chart shows the Face Bounding Boxes that were recognized by multiple software.
The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following groups were Boxes recognized by both Manual annotations and the Google API.

```{r Face-Bounding-Box-Data-Box, anchor="figure"}
ggplot(ALLmetaIMG, aes(x = factor(x = factor(type)), fill=type, y = size)) + geom_boxplot() + scale_y_continuous() +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Google","Animetrics","Manual","Microsoft","Skybiometry"))+ylab("Size of Face Bounding Boxes")+guides(fill=FALSE)

The box and whisker plot in 
`r figr("Face-Bounding-Box-Data-Box", TRUE, type="Figure")` shows the differences between the sizes of the 'Face Bounding Boxes' produced by each software. Where a 'Face Bounding Box' refers to the size of the square the software provided as a location in the image of a face that was detected. On average, Google maps the largest boxes around faces, and has the largest box recognized in the set. On average, the smallest Face Boxes are created by Skybiometry.

```{r I2, results=TRUE, caption="2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0014.png", anchor="figure"}
imagesList2<-as.list("2016_CT6_R02_FLopez_ESP_vs_GPella_ARG_MS227_clip.0009.png")
overlayGgplot(imagesList2, ALLmetaIMG, matchBox = FALSE)
```

The image above shows the smallest Face Bounding Box recognized. However visual inspection shows it only captures the player's eye and nose, not their whole face.

```{r I3, results=TRUE, caption="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMG, matchBox = FALSE)
```

>>>>

@@

      faceData <- faceData %>%
        mutate(x1 = minX, x2 = minX, x3 = maxX, x4 = maxX, x5 = minX,
               y1 = minY, y2 = maxY, y3 = maxY, y4 = minY, y5 = minY) %>%
        gather(corner, boxPos, x1:y5) %>%
        mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
        dplyr::select(-corner) %>% spread(posCoord, boxPos)

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
    }
  return(p)
  }
}

@@

# change this to facesVenn with binary information
ALLmetaIMGFaces<-ALLmetaIMG%>%
  filter(matchesManual) %>% 
  dplyr::select(-ID, -facecounter)%>%
  mutate(fileID = as.numeric(factor(file))) %>%
  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))

@@

```{r Trial-Image, caption="This is a player", message=TRUE, warning=TRUE, anchor="figure"}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, ALLmetaIMGFaces, matchBox = FALSE)
```

@@

## Regression

```{r}
ALLmetaIMGFaces
#for each face there
```

@@

-Google more than others

@@

`r figr("Face-Bounding-Box-Upset", TRUE, type="Figure")` Bar Chart shows the Face Bounding Boxes that were recognized by multiple software.
The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.

On average, Google maps the largest boxes around faces, and has the largest box recognized in the set. On average, the smallest Face Boxes are created by Skybiometry.

```{r I3, results=TRUE, caption="2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png", anchor="figure"}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
```
